High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-05-16 notebooks/gmsc.qmd
rerun

```{julia}
# Hyper:
_retrain = true

@@

```{julia}
λ₁ = 0.1
λ₂ = 0.1
λ₃ = 1.0
Λ = [λ₁, λ₂, λ₃]

@@

# Benchmark generators:
generator_dict = Dict(
    "Wachter" => WachterGenerator(λ=λ₁, opt=opt),
    "REVISE" => REVISEGenerator(λ=λ₁, opt=opt),
    "Schut" => GreedyGenerator(),
    "ECCCo" => ECCCoGenerator(λ=Λ, opt=opt, use_class_loss=use_class_loss),
)
```

>>>>

```{julia}
# Hyper:
_retrain = false

@@

```{julia}
λ₁ = 0.1
λ₂ = 0.5
λ₃ = 0.5
Λ = [λ₁, λ₂, λ₃]

@@

# Benchmark generators:
generator_dict = Dict(
    "Wachter" => WachterGenerator(λ=λ₁, opt=opt),
    "REVISE" => REVISEGenerator(λ=λ₁, opt=opt),
    "Schut" => GreedyGenerator(),
    "ECCCo" => ECCCoGenerator(
        λ=Λ, opt=opt, use_class_loss=use_class_loss,
        nsamples=10, nmin=10,
    ),
)
```

### 2023-05-16 notebooks/mnist.qmd
rerun

```{julia}
function _plot_eccco_mnist(
    x::Union{AbstractArray, Int}=x_factual, target::Int=target;
    λ=[0.25,0.75,0.75],
    temp=0.1,
    plt_order = ["MLP", "MLP Ensemble", "JEM", "JEM Ensemble"],
    opt = nothing,
    rng::Union{Int,AbstractRNG}=1234,
    T::Int = 100,
    use_class_loss::Bool = true,
)

@@

    # Generate counterfactuals using ECCCo generator:
    eccco_generator = ECCCoGenerator(
        λ=λ, 
        temp=temp, 
        opt=opt,
        use_class_loss=use_class_loss,
    )

@@

```{julia}
if _regen
    function plot_all_digits(rng=123;verbose=true,kwargs...)
        plts = []
        for i in 0:9
            for j in 0:9
                @info "Generating counterfactual for $(i) -> $(j)"
                plt = plot_mnist(i,j;kwargs...,rng=rng)
                !verbose || display(plt)
                plts = [plts..., plt]
            end
        end
        plt = Plots.plot(plts...; size=(img_height*10,img_height*10), layout=(10,10))
        return plt
    end
    plt = plot_all_digits(generator=eccco_generator)
    savefig(plt, joinpath(output_images_path, "mnist_eccco_all_digits.png"))
end
```

>>>>

```{julia}
function _plot_eccco_mnist(
    x::Union{AbstractArray, Int}=x_factual, target::Int=target;
    λ=[0.1,0.25,0.25],
    temp=0.1,
    plt_order = ["MLP", "MLP Ensemble", "JEM", "JEM Ensemble"],
    opt = nothing,
    rng::Union{Int,AbstractRNG}=1234,
    T::Int = 100,
    use_class_loss::Bool = true,
)

@@

    # Generate counterfactuals using ECCCo generator:
    eccco_generator = ECCCoGenerator(
        λ=λ, 
        temp=temp, 
        opt=opt,
        use_class_loss=use_class_loss,
        nsamples=10,
        nmin=10,
    )

@@

```{julia}
_regen_all_digits = false
if _regen_all_digits
    function plot_all_digits(rng=123;verbose=true,kwargs...)
        plts = []
        for i in 0:9
            for j in 0:9
                @info "Generating counterfactual for $(i) -> $(j)"
                plt = plot_mnist(i,j;kwargs...,rng=rng)
                !verbose || display(plt)
                plts = [plts..., plt]
            end
        end
        plt = Plots.plot(plts...; size=(img_height*10,img_height*10), layout=(10,10))
        return plt
    end
    plt = plot_all_digits(generator=eccco_generator)
    savefig(plt, joinpath(output_images_path, "mnist_eccco_all_digits.png"))
end
```
